
---
title: "Challenger O-Ring Failure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Challenger O-Ring Failure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(ggplot2)
library(emphatic)
```


Challenger O-Ring data
------------------------------------------------------------------------------

The raw challenger o-ring data shows the o-ring erosion and blow-by events on
shuttle launches leading up to the Challenger disaster.

This dataset was sourced from [tufte](http://williamwolff.org/wp-content/uploads/2013/01/tufte-challenger-1997.pdf)

Presented in order of launch date, there are obvious signs of damage on some flights,
but it's difficult to see trends in this presentation.

```{r}
library(dplyr)
library(ggplot2)
library(emphatic)
hl_opt_global(dark_mode = FALSE)

challenger
```


Ordering by temperature
------------------------------------------------------------------------------

When ordered by increasing temperature a trend is somewhat apparent in the
data i.e. lower temperatures have more incidents.

Finding this trend still requires close reading of the data.

```{r}
challenger %>% 
  arrange(temp)
```



First Iteration with `{emphatic}`
------------------------------------------------------------------------------

* Arrange by temperature
* Highlight the temperature range from cold to hot
* Highlight each row by the damage rating

The cluster of damage at lower temperatures is now much more visually apparent.

```{r}

challenger %>%
  arrange(temp) %>%
  hl(colour  = scale_color_viridis_c(option = 'B'), cols = 'temp') %>%
  hl(
    scale_color_gradient(low = 'pink', high = 'red'),
    rows = damage > 0,
    cols = damage,
    dest_cols = erosion:date
  ) 
```





Second Iteration with `{emphatic}`
------------------------------------------------------------------------------

* Expand temperature range to highlight the full limits of flight conditions
* Highlight the Challenger launch temperature in grey (31 degrees)
* It is now obvious that no real information is available at this low temperature,
  but all readings at low temperatures have issues.

```{r}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Expand temperature range to include challenger launch temperature
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
challenger_expanded <- challenger %>%
  mutate(temp = factor(temp, levels = 30:81)) %>%
  tidyr::complete(temp) %>%
  arrange(temp) %>%
  as.data.frame() %>%
  mutate(temp = as.numeric(levels(temp))[temp]) %>%
  select(flight, everything())


challenger_expanded %>% 
  hl(scale_color_viridis_c(option = 'B'), cols = temp) %>%
  hl(
    scale_color_gradient(low = 'pink', high = 'red'),
    rows = damage > 0,
    cols = damage,
    dest_cols = erosion:date
  ) %>%
  hl('grey50', rows = temp == 31, cols = erosion:date) %>%
  hl_opt(na = '')
```




