---
title: "Example - Matrix Highlighting - Correlation Matrix"
output: html_document
vignette: >
  %\VignetteIndexEntry{Example - Matrix Highlighting - Correlation Matrix}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(ggplot2)
library(emphatic)
```

```{r setup}
library(dplyr)
library(ggplot2)
library(emphatic)
hl_opt_global(dark_mode = FALSE)
```


The `cor()` function can calculate the correlation between the variables in a data.frame.

A question which is often asked of this correlation information, is which variables 
have a strong correlation (positive or negative)?

Standard Correlation Matrix
------------------------------------------------------------------------------

Hunting for the strong and weak correlations in the raw `cor()` output is difficult.

```{r}
cor(mtcars)
```


Correlation matrix with highlighting using `{emphatic}`
------------------------------------------------------------------------------

One way to highlight the correlations would be to colour the strong negative 
correlations in red, and the strong positive correlations in blue.

For this type of colouring, the `ggplot2` colour scale `scale_colour_gradient2()`
is a perfect fit.

Issue:  *everything* is now coloured - including 
locations with low correlation.

```{r}
cor(mtcars) %>%
  hl_mat(scale_colour_gradient2()) 
```

Apply colouring with `{emphatic}` to only locations with high correlation
------------------------------------------------------------------------------

The selection of locations to colour is controlled with the `selection` argument
to `hl_mat()`.


The result still isn't great because *everything* is now coloured - including 
locations with low correlation, as well as the diagonal (which is uninformative)

Issue: the diagonal of the matrix is still highlighted, 
but it is totally uninformative.

```{r}
cor(mtcars) %>%
  hl_mat(scale_colour_gradient2(), selection = abs(.x) > 0.7) 
```


Change text contrast
------------------------------------------------------------------------------

Since the magnitude of the correlations is now indicated by colour, we can
de-emphasise the text by reducing its contrast with the fill colour.

Also, the diagonals are now excluded from the colouring i.e. highlighting is
now further limited to where`row(.x) != col(.x)`

```{r}
cor(mtcars) %>%
  hl_mat(scale_colour_gradient2(), selection = abs(.x) > 0.7 & row(.x) != col(.x)) %>%
  hl_opt(text_contrast = 0.2)
```



