---
title: "Specifying Rows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Specifying Rows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(ggplot2)
library(emphatic)
hl_opt_global(dark_mode = FALSE)
```

```{r setup}
library(dplyr)
library(ggplot2)
library(emphatic)
hl_opt_global(dark_mode = FALSE)
```

```{r}
test_df <- head(mtcars, 10)
```

## Select all rows

```{r}
test_df %>%
  hl('skyblue')
```

```{r}
test_df %>%
  hl('skyblue', rows = NULL)
```

```{r}
test_df %>%
  hl('skyblue', rows = .all)
```

## Select rows by index

```{r}
test_df %>%
  hl('skyblue', rows = 2:5)
```

## Select rows by name

```{r}
test_df %>%
  hl('skyblue', rows = c('Mazda RX4', 'Datsun 710'))
```

## Select rows by rowname symbol

```{r}
test_df %>%
  hl('skyblue', rows = Valiant)
```

## Select rows by expression

```{r}
test_df %>%
  hl('skyblue', rows = mpg > 22)
```

## Select rows using `n()` and `row_number()`

```{r}
test_df %>%
  hl('skyblue', rows = row_number() > n()/2)
```

## Select rows using selectors like `tidyselect`

```{r}
test_df %>%
  hl('skyblue', rows = contains('hornet'))
```

```{r}
test_df %>%
  hl('skyblue', rows = starts_with('m'))
```

```{r}
test_df %>%
  hl('skyblue', rows = any_of(c('Valiant', 'Herbie', 'Datsun 710')))
```

Select rows using grouped data frames

------------------------------------------------------------------------

> Note: For grouped data frames, colours may be supplied for each group but will be chosen automatically if not. Additional customization can be done with the `cols` and `elem` arguments. Other arguments are not supported for grouped data frames.

```{r}
test_df %>%
  group_by(cyl) %>%
  hl()
```
